### 2017-02-05 levin_etal/reanalyses.rmd
minor tidying of levin et al reanalysis

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}

@@

# hist(D$Late - D$Mid)
w_late = wilcox.test(D$Late, D$Mid, alternative="greater", paired=T)$p.value
```

@@

```{r sorted_mid}
D[order(D[,4]),]

@@

```{r no_cteno}
D_no_ct = D[ ((D$Species_A != "Ctenophores") &   (D$Species_B != "Ctenophores")), ]
boxplot(as.matrix(D_no_ct[,3:5]))
wilcox.test(D_no_ct$Early, D_no_ct$Mid, alternative="greater", paired=T)
wilcox.test(D_no_ct$Late, D_no_ct$Mid, alternative="greater", paired=T)

@@

# Multiple plot function
#
# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
# - cols:   Number of columns in layout
# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
#
# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
# then plot 1 will go in the upper left, 2 will go in the upper right, and
# 3 will go all the way across the bottom.
#
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

@@

library(ggplot2)
library(reshape2)
library(grid)

@@

Dm = melt(D, id=c("Species_A", "Species_B"), variable.name = "phase", value.name = "similarity")
Dm_no_ct = melt(D_no_ct, id=c("Species_A", "Species_B"), variable.name = "phase", value.name = "similarity")

@@

pa = ggplot(Dm, aes(phase, similarity)) +
    geom_boxplot(outlier.shape=NA)+ # Outliers are drawn in bellow with jitter, so supress them here so they aren't duplicated
    scale_y_continuous(limits=limits) +
    geom_jitter(shape=16, position=position_jitter(0.2), alpha=alpha, color=color)

pa = pa + coord_flip() + ggtitle("(a) Original, with ctenophore in red")

pb = ggplot(Dm_no_ct, aes(phase, similarity)) +
    geom_boxplot(outlier.shape=NA)+ # Outliers are drawn in bellow with jitter, so supress them here so they aren't duplicated
    scale_y_continuous(limits=limits) +
    geom_jitter(shape=16, position=position_jitter(0.2), alpha=0.4)

pb = pb + coord_flip() + ggtitle("(b) New, without ctenophore")

#pa
#ggplotly()

@@

```{r DC_pre}
# Sample the columns for these two species
DC = Phase[,c(2,3)]
colnames(DC)

@@

DC = DC[(DC[,1]>0) & (DC[,2]>0),]
nrow(DC)
```

@@

```{r frac_4c_ce}
colnames(DC)[1]
ce = table(DC[,1])/sum(table(DC[,1]))
ce
```

@@

```{r frac_4c_dm}
colnames(DC)[2]
dm = table(DC[,2])/sum(table(DC[,2]))
dm
```

@@

>>>>

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
	library(ggplot2)
	library(tidyverse)
	library(grid)
```

@@

	# hist(D$Late - D$Mid)
	w_late = wilcox.test(D$Late, D$Mid, alternative="greater", paired=T)$p.value

@@

```{r sorted_mid}

	D[order(D[,4]),]

@@

```{r no_cteno}

	D_no_ct = D[ ((D$Species_A != "Ctenophores") &   (D$Species_B != "Ctenophores")), ]
	boxplot(as.matrix(D_no_ct[,3:5]))
	wilcox.test(D_no_ct$Early, D_no_ct$Mid, alternative="greater", paired=T)
	wilcox.test(D_no_ct$Late, D_no_ct$Mid, alternative="greater", paired=T)

@@

	# Multiple plot function
	#
	# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
	# - cols:   Number of columns in layout
	# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
	#
	# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
	# then plot 1 will go in the upper left, 2 will go in the upper right, and
	# 3 will go all the way across the bottom.
	#
	multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {

@@

@@

	phase_levels = c( "Early", "Mid", "Late" )

	Dm = D %>% 
		gather( Early, Mid, Late, key="phase", value="similarity" ) %>%
		mutate( phase=factor( phase, levels=phase_levels ) )

	Dm_no_ct =  D_no_ct %>% 
		gather( Early, Mid, Late, key="phase", value="similarity" ) %>%
		mutate( phase=factor( phase, levels=phase_levels ) )

@@

	pa = Dm %>% 
		ggplot( aes(x=phase, y=similarity) ) +
	    geom_boxplot(outlier.shape=NA) + # Outliers are drawn in bellow with jitter, so supress them here so they aren't duplicated
	    scale_y_continuous(limits=limits) +
	    geom_jitter(shape=16, position=position_jitter(0.2), alpha=alpha, color=color) + 
			coord_flip() + 
			ggtitle("(a) Original, with ctenophore in red")

	pb = Dm_no_ct %>% 
		ggplot( aes(x=phase, y=similarity)) +
	    geom_boxplot(outlier.shape=NA)+ # Outliers are drawn in bellow with jitter, so supress them here so they aren't duplicated
	    scale_y_continuous(limits=limits) +
	    geom_jitter(shape=16, position=position_jitter(0.2), alpha=0.4) + 
			coord_flip() + 
			ggtitle("(b) New, without ctenophore")

@@

```{r DC_pre}

	# Sample the columns for these two species
	DC = Phase[,c(2,3)]
	colnames(DC)

@@

	DC = DC[(DC[,1]>0) & (DC[,2]>0),]
	nrow(DC)

@@

```{r frac_4c_ce}

	colnames(DC)[1]
	ce = table(DC[,1])/sum(table(DC[,1]))
	ce

@@

```{r frac_4c_dm}

	colnames(DC)[2]
	dm = table(DC[,2])/sum(table(DC[,2]))
	dm

@@

### Matrix occupancy

```{r gene_phase_matrix}

	n_species_sampled = apply( Phase, 1, function(x) sum( x > 0 ) )

	phase_sub = Phase[ n_species_sampled >= 2, ]

	hist( n_species_sampled )

There were `r nrow(Phase)` gene in the original data file. `r sum(n_species_sampled == 0)` of these had no phase annotations for any species. `r nrow(phase_sub)` had phase annotations for 2 or more species.
